The Name of the Title Is Hope

### 2024-11-10 paper/paper.tex
Added some more

@@

We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by Ryan McKenna\cite{Ullman2022,McKenna2022,McKenna_privatePGM,mckenna2021winning,mckenna2019graphical}.

The competition considers marginals of the synthetic data. The idea of marginal-based synthetic data generation is to create a model whose marginals of samples are similar to the marginals of the original data. For example, suppose we have an original database and it's 2-way marginal on sex(Male,Female) and race(White,Black) is as shown in Table~\ref{tab:marginal-example}.

@@

@@

\subsection{Implementation}

>>>>

We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by Ryan McKenna\cite{Ullman2022,McKenna2022,McKenna_privatePGM,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.

The research is implemented in Python Jupyter notebooks and is publicly available.

@@

The NIST competition considers marginals of the synthetic data. The idea of marginal-based synthetic data generation is to create a model whose marginals of samples are similar to the marginals of the original data. For example, suppose we have an original database with attributes including sex(Male,Female) and race(White,Black) and its 2-way marginal on them is as shown in Table~\ref{tab:marginal-example}. The marginal of the synthetic data is supposed to be similar to that of the original database.

@@

The synthesis framework is three-fold; namely, select-measure-generate. We first select the important marginals to preserve, measure them by adding differential private noise, and then generate synthetic data. Underneath the hood, the tool employs a Markov random field(MRF) and the select step corresponds to marking cliques in a MRF.

For the select step, we followed the techniques used by Ryan McKenna in the competition by calculating the mutual information(MI) of the given database and then create a maximum spanning tree(MST) with edge weights being the MIs. We further added edges according to a fraction of the upper bounds of each MI by calculating the Shannon entropies.

For the measure and generate step, we simply followed the examples provided in the tool's repository. We added Gaussian noise to the marginals. we spent half of the privacy budget $\epsilon = 1$ on all 1-way marginals and the other on the MRF cliques. And then we generate synthetic data of size similar to the original database. By \cite{mckenna2021winning}, this procedure satisfies $(\alpha,\frac{\alpha}{2 \sigma^2})$-RDP for all $\alpha \geq 1$.

@@

We used the fairness checker from \cite{yuan2024ensuring}. We set the privileged predicate $\priv$ to male and the positive predicate $\pos$ to the positive prediction of each of the corresponding dataset.

\subsection{Test Models}

We extracted various models from Kaggle. They are finetuned to perform well on the original dataset. For one, a random forest model is finetuned by searching hyperparameters settings\cite{Ipbyrne2023}. For another, a logistic regression model is finetuned by performing principal component analysis\cite{Prashant1112023}.
